Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
Figure5 Ready

@@

Kernel density estimation plots with kde1d

```{r fig.width=9, fig.height=3.5, include = FALSE}
library(kde1d)

@@

xmax <- 1500
ncurves <- 50

@@

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> cp.dens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> pp.dens

@@

cp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        axis.title.y = element_blank()) -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        axis.title.y = element_blank()) -> pp.tail

np.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        axis.title.y = element_blank()) -> np.tail

@@

```{r KernelGrid}
plot_grid(kernelcurvesfig, kernel_tails_fig, ncol = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)
```

```{r}
# all density means

ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  # Everything after this line is the confidence intervals
  #   stat_function(fun = dweibull, args = list(shape = CIshape$low[1], scale = CIscale$low[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$low[2], scale = CIscale$low[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$low[3], scale = CIscale$low[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
  # lims(x = c(0, 1500), y = c(0, 0.006)) +
  #     stat_function(fun = dweibull, args = list(shape = CIshape$high[1], scale = CIscale$high[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$high[2], scale = CIscale$high[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$high[3], scale = CIscale$high[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
  lims(x = c(0, 1500), y = c(0, 0.0062)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
#coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0002)) +
    NULL
```

```{r}
ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  lims(x = c(0, 1500), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0003))
```

```{r eval=FALSE}
CIdata %>% 
  filter(., param == "shape") %>% 
  ggplot(., aes(x  = model, y = mean)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Value", x = "Shape") +
  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> ShapeCI

CIdata %>% 
  filter(., param == "scale") %>% 
  ggplot(., aes(x  = model, y = mean)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Value", x = "Scale") +
  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> ScaleCI

plot_grid(ShapeCI, ScaleCI)

# The proportion of shape parameter values above the sampling distribution is 
prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)
```

@@

Dispersal Kernels

ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  cp_lines +
  pp_lines +
  np_lines +
  lims(x = c(0, 1250)) +
  theme_bw()

```{r}
cp_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))

>>>>

```{r loadingData}

@@

```{r Kde1dEstimates, include = FALSE}
library(kde1d)

@@

```{r RunPurrrCurves}

xmax <- 1500
ncurves <- 200

@@

ggplot() +
  cp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> cp.dens

ggplot() +
  pp_lines +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
  lims(x = c(0, xmax), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        panel.grid.major = element_blank()) +
  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
  NULL -> pp.dens

@@

cp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "white")) +
  labs(y = "") -> cp.tail

pp.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "white")) +
  labs(y = "") -> pp.tail

np.dens +
  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
  theme(panel.background = element_rect(fill = backgroundcol),
        panel.grid = element_line(color = "white")) +
  labs(y = "") -> np.tail

@@

```{r eval = FALSE}
# all density means

ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  # Everything after this line is the confidence intervals
  #   stat_function(fun = dweibull, args = list(shape = CIshape$low[1], scale = CIscale$low[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$low[2], scale = CIscale$low[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$low[3], scale = CIscale$low[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
  # lims(x = c(0, 1500), y = c(0, 0.006)) +
  #     stat_function(fun = dweibull, args = list(shape = CIshape$high[1], scale = CIscale$high[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$high[2], scale = CIscale$high[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = CIshape$high[3], scale = CIscale$high[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
  lims(x = c(0, 1500), y = c(0, 0.0062)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
#coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0002)) +
    NULL

ggplot() +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
  lims(x = c(0, 1500), y = c(0, 0.006)) +
  theme_bw() +
  labs(y = "Density", x = "Dispersal (m)") +
  coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0003))
```

```{r ParamCIs}
CIdata %>% 
  filter(., param == "shape") %>% 
  ggplot(., aes(x  = model, y = mean, color = model)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Shape value", x = "Model") +
  scale_color_manual(values = fig.5col) +
  theme_bw() +
  theme(legend.position = "none") -> ShapeCI

CIdata %>% 
  filter(., param == "scale") %>% 
  ggplot(., aes(x  = model, y = mean, color = model)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Scale value", x = "Model") +
  scale_color_manual(values = fig.5col) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_blank()) -> ScaleCI

CIparams_figure <- plot_grid(ScaleCI, ShapeCI, nrow = 2)
#CIparams_figure
# # The proportion of shape parameter values above the sampling distribution is 
# prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
# prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
# prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)
```

```{r MeanVar}

violincolor <- "lightgray"

joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = meanweib)) +
  geom_violin(color = violincolor, fill = violincolor) +
  geom_boxplot(width = 0.1, aes(color = model)) +
  scale_color_manual(values = fig.5col) +
  # geom_violin() +
  # geom_jitter(data = joint_weib %>% 
  #               group_by(model) %>% 
  #               sample_n(200),
  #             position = position_jitter(0.1)) +
  #geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Est. Mean", x = "Model") +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") +
  NULL -> weib_mean

joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = varweib)) +
    geom_violin(color = violincolor, fill = violincolor) +
  geom_boxplot(width = 0.1, aes(color = model)) +
  scale_color_manual(values = fig.5col) +
  # geom_violin() +
  # geom_jitter(data = joint_weib %>% 
  #               group_by(model) %>% 
  #               sample_n(200),
  #             position = position_jitter(0.1)) +
  labs(y = "Est. Variance", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") +
  NULL-> weib_variance

MeanVar_figure <- plot_grid(weib_mean, weib_variance, nrow = 2, align = "v")
#MeanVar_figure
```

```{r Figure5, fig.width=12, fig.height=7}

plot_grid(kernelcurvesfig, kernel_tails_fig, CIparams_figure, MeanVar_figure, ncol = 4, rel_widths = c(0.9, 1, 0.3, 0.6),
          labels = c("A)", "B)", "C)", "D)"), hjust = -0.5, vjust = 1, label_size = 10)

@@

```{r CIkernels, eval = FALSE}
cp_lines <- purrr::map(seq(1:100), function(y)
  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))
